\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-22 journalWallFriction/theory2robAlgs.tex
small updates showing todos in red

The $\Delta$ configuration space is a set of all possible $\Delta p$ values.
 $\Delta$ configuration spaces for a representative set of workspaces are shown in Fig.~\ref{fig:polygon}. The \emph{reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first.
 Fig.~\ref{fig:regionMove} shows the starting and ending relative positions as $\Delta s$ and $\Delta g$ in the $\Delta$ configuration space.  The next subsections give procedures to compute the reachable set.% in Fig.~\ref{fig:regionMove}.% The reachable set is the part of $\Delta$ configuration space where if one particle touches a wall in a specific location, the other particle can make the required relative distance without causing the touching particle to move. We will discuss how to make reachable sets in the next subsections.

@@

\subsection{Convex Polygonal Workspaces: Reachable Set}

@@

\subsection{Circular Workspaces: Reachable Set}

>>>>

The $\Delta$ configuration space is a set of all possible $\Delta p$ values.
 $\Delta$ configuration spaces for a representative set of workspaces are shown in Fig.~\ref{fig:polygon}. The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first.
 Fig.~\ref{fig:regionMove} shows the starting and ending relative positions as $\Delta s$ and $\Delta g$ in the $\Delta$ configuration space.  The next subsections give procedures to compute the reachable set.% in Fig.~\ref{fig:regionMove}.% The reachable set is the part of $\Delta$ configuration space where if one particle touches a wall in a specific location, the other particle can make the required relative distance without causing the touching particle to move. We will discuss how to make reachable sets in the next subsections.

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%\
\subsection{$\Delta$ Configuration Space}

 Given an $n$-sided convex polygon $P$, the $\Delta$ configuration space is an $2n$-sided convex polygon.
 A special case is for even-sided regular polygons, in which half the sides align and the $\Delta$ configuration space  is $n$-sided.

 \textcolor{red}{[INSERT PROCEDURE]}\\

 \textcolor{red}{    Describe how to generate a $\Delta$ Configuration Space for polygon $P$.}

 \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\

\subsection{Convex Polygonal Workspaces: 2-Move Reachable Set}

@@

\subsection{Circular Workspaces: 2-Move Reachable Set}
